Tools for identifying unexpectedly low microfossil count sums

### 2020-06-11 Rmd/count_check_MS.Rmd
edit hershop bog with Patty thesis

The pollen data from the Neotoma database included over `r pollen_summ$n_assemblages` assemblages in `r pollen_summ$n_datasets %>% format()` datasets. 
Nearly all assemblages have singletons (`r pollen_summ$p_singletons`%) and a greatest common divisor of one (`r pollen_summ$p_gcd1`%). 
The assemblages with a greatest common divisor above one are not randomly distributed among the datasets: only `r pollen_summ$dataset_gcd1`% of the datasets have any such assemblages.
Some datasets with a high proportion of assemblages with a greatest common divisor above one are older datasets which may, despite the available metadata, have been digitised with the loss of rare taxa and precision.
For example, all but `r hershop_pollen_summ$has_singleton %>% word()` of the `r hershop_pollen_summ$n` assemblages in the archived pollen data from Hershop Bog Texas have a greatest common divisor of two or more (the exception has a single singleton and is otherwise divisible by two). 
Discrepancies between the archived data and the original paper [@Larson_1972] including an incomplete species list and the inclusion of fern spores in the count sum of two hundred grains strongly suggest that these data have been digitised.
For most purposes, such digitised data are perfectly adequate.

>>>>

The pollen data from the Neotoma database included over `r pollen_summ$n_assemblages` assemblages in `r pollen_summ$n_datasets %>% format()` datasets. 
Nearly all assemblages have singletons (`r pollen_summ$p_singletons`%) and a greatest common divisor of one (`r pollen_summ$p_gcd1`%). 
The assemblages with a greatest common divisor above one are not randomly distributed among the datasets: only `r pollen_summ$dataset_gcd1`% of the datasets have any such assemblages.
Some datasets with a high proportion of assemblages with a greatest common divisor above one are older datasets which may, despite the available metadata, have been back-transformed from percent data or digitised with the loss of rare taxa and precision.
For example, all but `r hershop_pollen_summ$has_singleton %>% word()` of the `r hershop_pollen_summ$n` assemblages in the archived pollen data from Hershop Bog, Texas have a greatest common divisor of two or more (the exception has a single singleton and is otherwise divisible by two). 
The original data [@Patty1968] were counted to exactly 200 pollen grains and fern spores. 
It seems likely that the data were converted to percent, rounded and then back-tranformed to counts.
For most purposes, such back-transformed or digitised data are perfectly adequate.
